---
title: "Edgar Anderson’s Iris Data"
output: 
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Description

This famous (Fisher's or Anderson's) iris data set gives the measurements in centimeters of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. The species are *Iris setosa*, *versicolor*, and *virginica*.

## Usage

`iris`

## Format

`iris` is a data frame with 150 cases (rows) and 5 variables (columns) named: 
* `Sepal.Length` 
* `Sepal.Width` 
* `Petal.Length` 
* `Petal.Width` 
* `Species`

## Source

Anderson, Edgar (1935). "The irises of the Gaspe Peninsula." *Bulletin of the American Iris Society*, **59**: 2--5. Fisher, Ronald A. (1936). "The use of multiple measurements in taxonomic problems." *Annals of Eugenics*, **7** (Part II): 179--188.

## Examples

We investigate the Sepal and Petal leaves for the three species in the Iris data:

```{r summary}
summary(iris)
```
To examine the Sepal leaves, we select the length and the width:

```{r leaves}
llen <- iris$Sepal.Length
lwid <- iris$Sepal.Width
```

Then we plot the data:

```{r leaves_plot}
plot(llen, lwid, xlab = "Length", ylab = "Width",
pch = 20, col = as.numeric(iris$Species))
legend("bottomright", legend = levels(iris$Species), col = 1:3, pch = 20)
```

We can also select the Petal leaves:

```{r petals}
llen <- iris$Petal.Length
lwid <- iris$Petal.Width
```

```{r petals_plot, echo = FALSE}
plot(llen, lwid, xlab = "Length", ylab = "Width",
pch = 20, col = as.numeric(iris$Species))
legend("bottomright", legend = levels(iris$Species), col = 1:3, pch = 20)
```